---
title: "Introduction to Binomial Package"
author: "Jiaxin Chen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(binomial)
```

## Binomial Distribution

The package `"binomial"` is a minimal implementation for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc.

## Function bin_choose()

Function `bin_choose()` is used to calculate the number of combinations in which k successes can occur in n trials.
```{r}
bin_choose(n = 5, k = 2)
```


## Function bin_probability()

Function `bin_probability()' is used to calculate the probability of k successes in n trials of a binomial distribution. 
```{r}
# probability of getting 2 successes in 5 trials
# (assuming prob of success = 0.5) 
bin_probability(success = 2, trials = 5, prob = 0.5)
```


## Function bin_distribution()

Function 'bin_distribution()` is used to create a data frame with the probability distribution: sucesses in the first column, probability in the second column

```{r}
 # binomial probability distribution
bin_distribution(trials = 5, prob = 0.5)
```

Also, we can create a barplot to display the probability histogram of a binomial distribution object "bindis".
```{r}
# plotting binomial probability distribution
dis1 <- bin_distribution(trials = 5, prob = 0.5) 
plot(dis1)
```


## Function bin_cumulative()
Use the function `bin_cumulative()` to display a data frame with both the probability distribution and the cumulative probabilities: sucesses in the first column, probability in the second column, and cumulative in the third column.
```{r}
 # binomial cumulative distribution
bin_cumulative(trials = 5, prob = 0.5)
```

Also, plot a graph of a binomial cumulative distribution.
```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5) 
plot(dis2)
```


## Function bin_variable()

Use function `bin_variable()` to print a summary of binomial random variable object.
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3) 
binsum1 <- summary(bin1)
binsum1
```


## Functions of measures

Finally, use the functions for each of the summary measures: e.g. bin_mean(), bin_variance(), etc. to displace the measurement of a binomial distribution.
```{r}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```







